Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-08-28 Article.tex
Corrections on Section 3 and conclusions + figures

The precision of the critical DRX conditions is closely linked to the method of obtaining the curve $\theta(\sigma)$.
Using experimental raw data directly does not yield functional curves, thus smoothing the $\sigma(\varepsilon)$ \OP{I suggest the following writing: $\sigma=f(\varepsilon)$ instead of $\sigma(\varepsilon)$} \textcolor{red}{Done throughout the paper} curve as much as possible or approximating it with a polynomial function that can reproduce the curve and deducing the $\theta(\sigma)$ curve from it is commonly used.
The drawback of both of these methods is that they do not always ensure a satisfactory smoothing of the curve $\sigma(\varepsilon)$.
Nevertheless, the Universal Approximator, Artificial Neural Networks (ANN), has demonstrated effectiveness in various domains, such as predicting the flow behavior of materials.
Hence, this study offers a replacement of the two smoothing methods with an ANN to procure the critical conditions for DRX.
In other words, the proposed method suggests using an artificial neural network (ANN) to directly model the relationship between stress $\sigma$ and rate hardening $\theta$, removing the need for explicit smoothing of experimental data.
By properly training the ANN with relevant data, it can learn the underlying relationship between stress and dynamic recrystallization (DRX), ultimately providing a more precise estimation of the critical conditions for DRX.

@@

The material used for this study is a medium-carbon steel with the chemical composition presented in Table \ref{tab:Composition}.
\begin{table}[H]
\centering
\caption{Chemical composition of medium carbon steel. Fe = balance.}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{LCCCCCCC}
\hline
\textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\
\hline
\textbf{Wt~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
\hline
\end{tabularx}
\label{tab:Composition}
\end{table}
Hot compression tests were conducted on cylinders with an initial diameter of $\phi=10$~mm and a height of $h=15$~mm using a Gleeble-3800 thermomechanical simulator.
The tests were conducted at 5 temperature levels (ranging from $1050\celsius$ to $1250\celsius$) and 6 strain rates (ranging from $0.001~\ps$ to $5~\ps$).
The imposed displacement was set to $d=6$~mm, resulting in a reduction of $40\%$ of the initial height.
To reduce friction during testing, thin tantalum sheets were used as a lubricant on the contact surface of the anvils and specimens.
In order to remove thermal gradients, the samples were heated at a speed of $2$\celsius/s until reaching a temperature of $1260\celsius$, then held at that temperature for $5$~minutes.
They were subsequently cooled down to the test temperature at a speed of $1$\celsius/s and left at a consistent temperature for $1$~minute prior to being formed.
During compression, the sample temperature is maintained at a constant level through the machine's thermal control system.
Subsequently, the structure is frozen at a fast pace in order to preserve the microstructure for future analysis.

@@

No activation function was used for the output neuron of the ANN, as is typically omitted in regression applications.
The chosen architecture for our application consists of two hidden layers, one with 7 neurons and the other with 5 neurons, as illustrated in Figure \ref{fig:ANN-7-5}.
To calculate the number of internal parameters $N_{int}$ in the model, where $n$ and $m$ represent the number of neurons in the first and second hidden layers, respectively, the following formula may be used: $N_{int}=m(2+n)+2n+1$.
So that for a $7-5$ network, $N_{int}=60$.
\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/ANN-7-5}
\caption{Two hidden layers artificial neural network architecture with 1 input neuron (green) and 1 output neuron (red).}
\label{fig:ANN-7-5}
\end{figure}
The Python program used for training the neural network was created with the dedicated Python library, Tensorflow \cite{Abadi-2016}.
The training phase employed the Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015}.

@@

It is evident that using the ANN model to depict the $\sigma(\varepsilon)$ curve is superior to using an $11^{th}$ order polynomial fit, as demonstrated by the lower estimated error.
Thus, this architecture of the ANN model is used for all subsequent curves, resulting in the deduction of the hardening $\theta(\sigma)$ curves, which illustrate the stress change rate relative to strain ($\frac{\partial \sigma}{\partial \varepsilon}$).
An example of calculating the hardening curve for a single temperature is presented in Figure \ref{fig:AnnTheta}, while an overview of the remaining temperatures can be found in Figure \ref{fig:nThetaOP}. \OP{Have to improve this later} \textcolor{red}{Okay}.
The identical process applies to all 20 stress/strain curves.
These curves deliver essential data regarding the critical stresses and strains required for predicting DRX in the subsequent analysis.

@@

\begin{table}[h!]
\centering
\caption{Critical conditions based on the proposed approach.\OP{Caption changed} \textcolor{red}{Okay}}\vspace{-1mm}
\begin{tabular}{cccccc}
\toprule
$\mdot{\varepsilon}$ ($\ps$) & $T$ (\celsius) & $\varepsilon_p$ & $\sigma_p$ (MPa) &  $\varepsilon_c$ & $\sigma_c$ (MPa) \\
\hline
 & $1050$ & $0.178$ & $37.862$ & $0.083$ & $33.050$\\
 & $1100$ & $0.143$ & $29.770$ & $0.067$ & $25.648$\\
$0.001$ & $1150$ & $0.124$ & $23.330$ & $0.051$ & $19.116$\\
 & $1200$ & $0.102$ & $19.373$ & $0.039$ & $16.244$\\
 & $1250$ & $0.084$ & $13.883$ & $0.035$ & $11.302$\\

 & $1050$ & $0.281$ & $57.915$ & $0.131$ & $51.602$\\
 & $1100$ & $0.228$ & $46.107$ & $0.108$ & $40.495$\\
$0.01$ & $1150$ & $0.195$ & $38.249$ & $0.086$ & $33.435$\\
 & $1200$ & $0.172$ & $30.991$ & $0.076$ & $26.718$\\
 & $1250$ & $0.139$ & $24.739$ & $0.051$ & $20.004$\\

 & $1050$ & $0.571$ & $91.413$ & $0.244$ & $83.814$\\
 & $1100$ & $0.430$ & $72.662$ & $0.194$ & $65.259$\\
$0.1$ & $1150$ & $0.344$ & $57.774$ & $0.160$ & $51.723$\\
 & $1200$ & $0.299$ & $48.473$ & $0.136$ & $42.386$\\
 & $1250$ & $0.259$ & $40.195$ & $0.119$ & $35.277$\\

 & $1050$ & $0.700$ & $127.17$ & $0.577$ & $116.10$\\
 & $1100$ & $0.700$ & $106.61$ & $0.329$ & $94.510$\\
$1$ & $1150$ & $0.700$ & $89.525$ & $0.268$ & $89.067$\\
 & $1200$ & $0.700$ & $72.270$ & $0.178$ & $57.929$\\
 & $1250$ & $0.393$ & $59.992$ & $0.112$ & $54.066$\\
\bottomrule
\end{tabular}
\label{tab:OPparams}
\end{table}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/picDRX}
\caption{Schematic diagram of three stages during DRX, nucleation, nucleus growth and grain contact \cite{wan2017experimental}. \OP{Is it a copy/paste from a publication? If so, you can't put it as it!} \textcolor{red}{Of course it was taken from publication as reference is mentioned. Please, I will appreciate if you could rearrange it as it would have been made. Thanks !}}
\label{fig:DRXschema}
\end{figure}
The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
The predicted volumetric fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model  \cite{wan2017experimental} \OP{REF?} \textcolor{red}{Done}, commonly known as the JMAK model, expressed by the following equation:
\begin{equation}
X_{drx}^{p} = 1 - \exp\left[ -k\left(\frac{\varepsilon - \varepsilon_c}{\varepsilon_p}\right)^{n_k}\right]
\label{eq:drxpred}
\end{equation}
With $\varepsilon_c$ and $\varepsilon_p$ as the critical and peak strain respectively; $k$ and $n_k$ as the model's parameters and the experimental equivalence of this volumic fraction of DRX is given by :
\begin{equation}
X_{drx}^{e} = \frac{\sigma_p-\sigma}{\sigma_p-\sigma_{s}}
\label{eq:drxexp}
\end{equation}

@@

The curves of $X_{drx}(\varepsilon)$ are provided in Figure \ref{fig:nDRX} using the critical conditions calculated by the Poliak method.
From this figure, it can be observed that the predictions align well with the experimental data, thus demonstrating the validity of the used model. \OP{I don't agree!} \textcolor{red}{Please have a look on Figure \ref{fig:nDRX} for more comprehension}
These results will therefore be used subsequently in the simulation section.
\begin{figure}[H]
\centering
\includegraphics[width=0.99\columnwidth]{Figures/nDRX1}
\caption{Comparison between DRX experimental data and JMAK model based prediction. \OP{I don't see the comparison? Is there many superposed curves ???} \textcolor{red}{As I said in my previous mail, I was writing the paper like the experimental data are already provided. Everything is okay now, I think !}}
\label{fig:nDRX}
\end{figure}

@@

In this section, the numerical validation of the previously performed dynamic recrystallization identification will be addressed.
To achieve this, it is essential to establish a constitutive law capable of accurately predicting the plastic deformation of the material.
In our prior publication (Tize Mha \eal \cite{TizeMha-2023}), a comparison between analytical constitutive laws and neural network based approach was conducted, resulting in the identification of an ANN model as the suitable choice for this material.
As a result, this section comprises a two-fold focus: firstly, a recapitulation of the ANN based constitutive law identification, as presented in the previous article; and secondly, the integration of this identified ANN model with the JMAK model for predicting dynamic recrystallization behavior.

@@

In general terms, flow stress $\sigma$ is a non-linear function of the strain $\varepsilon$, increasing with the strain rate $\mdot\varepsilon$, but decreasing with increasing temperature $T$.
The model can therefore be described as an elastoplastic model with the influence of strain rate and temperature.
This type of behavior generally leads to Johnson-Cook \cite{Johnson-1983}, Zerilli Armstrong \cite{Zerilli-1987}, Hansel Spittle \cite{Hensel-1978} or Arrhenius \cite{Sellars-1966} flow law type.
Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.
As reported by Tize Mha \eal \cite{TizeMha-2023}, Johnson-Cook, Zerilli Armstrong or Hansel Spittle type models, while providing a more or less faithful reproduction of material behavior at strain rates above $1~\ps$, do not take into account the softening due to DRX visible on experimental curves for strain rates below $1~\ps$ as reported in Figure \ref{fig:RawData}.
Indeed, for the lowest strain rates, the flow stress $\sigma$ increases with strain $\varepsilon$ up to a value of around $\varepsilon=0.2$ to $0.3$ and then decreases to maintain a more or less constant value until the end of the test.
Only the Arrhenius model can more or less account for this softening at low strain rates.
As proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023} and Tize Mha \eal \cite{TizeMha-2023}, an effective alternative is to use a flow law defined by an artificial neural network trained directly on experimental data from compression tests.
Correctly defining the hyperparameters of this neural network (number of hidden layers, number of neurons, activation functions, etc.) allows us to obtain a flow law that faithfully reproduces the data obtained from compression tests.

According to the method proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023}, we developed in Tize Mha \eal \cite{TizeMha-2023} a two hidden layers ANN based flow law whose general structure is reported in Figure \ref{fig:ANN-2HL}.
This ANN contains an input layer of three neurons corresponding to the entries of the model ($\varepsilon$, $\mdot\varepsilon$ and $T$), an output layer with one neuron ($\sigma$), and $2$ hidden layers.

All details about the artificial neural network, setup of the experimental data and the training method is reported the paper proposed by Pantalé \cite{Pantale-2023}.
%Thus, all the neurons of the $k^{th}$ layer are connected to all the neurons of the ($k-1^{th}$) layer, as shown in~Figure~\ref{fig:ANN-2HL}.

@@

We again used the Tensorflow library for the development of the training program, and the ADAM optimizer was used for the training phase.
The provided database presented in Section \ref{subsec:ExperimentalProcedure} consists of $21,030$ quadruplets of strain ($\varepsilon$), strain rate ($\mdot\varepsilon$), temperature ($T$) and stress ($\sigma$) values.
%The training data were those from the tests presented in Section \ref{sec:ComTestResults} and were composed of $21,030$ quadruplets of ($\varepsilon$, $\mdot\varepsilon$, $T$, $\sigma$) values.

We selected 6 different networks, named 3-$n$-$m$-1, where $n$ is the number of neurons in the first hidden layer and $m$ is the number of neurons in the second hidden layer, to show the importance of selecting the adequate number of neurons in the two layers.

The training was performed on the basis of $5000$ epochs of the experimental dataset.
It took $40$~min of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GB of RAM and an Intel 4-core i7-10510U processor to obtain the converged parameters of the ANN model.

Figure \ref{fig:ANN-conv} shows the evolution of the training error defined by the $\log_{10}$ of the internal $\RMSE$ during the training phase and Table \ref{tab:Errors} summarizes the final values of this criterion, along with the final values of the $\MARE$ and the $\RMSE$ for the 6 configurations of the neural network.
On the basis of those results, we have selected the 3-15-7-1 network for further study, as it has the best convergence evolution and the lowest final error values ($\MARE=0.62\%$ and $\RMSE=0.38~\MPa$), while keeping a reasonable number of internal parameters ($N_{int}=180$).

@@

\begin{table}[H]
\caption{Architecture and accuracy coefficients for all the proposed networks.}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\begin{tabularx}{\textwidth}{LCCCCCC}
\toprule
\textbf{Coefficients} & \textbf{3-7-5-1} & \textbf{3-9-4-1} & \textbf{3-9-5-1} & \textbf{3-9-7-1} & \textbf{3-13-7-1} & \textbf{3-15-7-1} \\
\hline
$N_{int}$ & $74$ & $81$ & $92$ & $114$ & $158$ &$180$\\
\toprule
$\log_{10}(\RMSE)$ & $-2.40$ & $-2.42$ & $-2.38$ & $-2.45$ & $-2.50$ & $-2.58$ \\
$\MARE(\%)$ & $1.13$ & $1.05$ & $1.08$ & $0.91$ & $0.75$ & $0.62$ \\
$\RMSE(\MPa)$ & $0.59$ & $0.57$ & $0.65$ & $0.55$ & $0.46$ & $0.38$ \\
\bottomrule
\end{tabularx}
\label{tab:Errors}
\end{table}

\begin{figure}[H]
\centering
\includegraphics[width=0.9\columnwidth]{Figures/CompExpANN-3-15-7-1}
\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma$ by the 3-15-7-1 ANN model.}
\label{fig:ANN-3-15-7-1}
\end{figure}
This model will be used as the material flow law for the numerical simulations presented in Section \ref{subsec:DRXSimulation}.

@@

In order to assess the effectiveness of the implementation of the DRX model presented in the previous sections, a compression test is simulated in this section.
For this purpose, the material used for this simulation is a medium-carbon P20 iron alloy, which was used for the identification of this model.
An axisymmetric Finite Element Method (FEM) model of hot cylinder compression with a height of $15$ mm and a diameter of $5$ mm is used, as shown in Figure \ref{fig:Mesh}.
The frictional coefficient at the material/Die interface was assumed to be $0.2$ \cite{zhang2019elevated,sun2020kinetique}.
The mesh consists of 986 CAX4R elements (4-node axisymmetric bi-linear quadrilateral elements with reduced integration and hourglass control).
The FEM model is simulated using Abaqus/Implicit due to the computation time related to the low strain rates.
A displacement of $60\%, ~45\%, ~30\%$ and $15\%$ mm of the total height is imposed on the upper part of the cylinder during the compression along the vertical axis of the specimen.
The radial displacement $u_r$ of the upper part of the specimen is left free, while its axial displacement $u_z$ is imposed.
The lower part of the cylinder remains fixed during the simulation.
The effect of reducing the cylinder in combination with strain rate and temperature effect has been also evaluated in this simulation, and conclusions have been drawn.
For this simulation, three temperatures ($1050\celsius$, $1150\celsius$, and $1250\celsius$) and four strain rates ($0.001~\ps$, $0.01~\ps$, $0.1~\ps$ and $1.0~\ps$) are considered.
\begin{figure}[H]
\centering
\includegraphics[width=0.6\columnwidth]{Figures/CyCompression2}
\caption{Numerical model for the compression test}
\label{fig:Mesh}
\end{figure}

@@

In this study, we have harnessed the capabilities of ANN technique to gain a profound understanding of the dynamic recrystallization process and its evolution under varying conditions.
The integration of ANN modeling, fundamental material models, simulation software, and experimental validation has led to a comprehensive framework that contributes significantly to the field of materials science and engineering.
Initially, we successfully employed a ANN model to fit flow stress curves, enabling the prediction of critical conditions using the Poliak model.
Doing this has allowed us to accurately anticipate the conditions at which the DRX process initiates, providing an invaluable tool for anticipating material behavior under specific deformation scenarios.

>>>>

The precision of the critical DRX conditions is closely linked to the method of obtaining the curve $\theta(\sigma)$.
Using experimental raw data directly does not yield functional curves, thus smoothing the $\sigma(\varepsilon)$ \OP{I suggest the following writing: $\sigma=f(\varepsilon)$ instead of $\sigma(\varepsilon)$} \textcolor{red}{Done throughout the paper} curve as much as possible or approximating it with a polynomial function that can reproduce the curve and deducing the $\theta(\sigma)$ curve from it is commonly used.
The drawback of both of these methods is that they do not always ensure a satisfactory smoothing of the curve $\sigma(\varepsilon)$.
Nevertheless, the Universal Approximator, Artificial Neural Networks (ANN), has demonstrated effectiveness in various domains, such as predicting the flow behavior of materials.
Hence, this study offers a replacement of the two smoothing methods with an ANN to procure the critical conditions for DRX.
In other words, the proposed method suggests using an artificial neural network to directly model the relationship between stress $\sigma$ and rate hardening $\theta$, removing the need for explicit smoothing of experimental data.
By properly training the ANN with relevant data, it can learn the underlying relationship between stress and dynamic recrystallization (DRX), ultimately providing a more precise estimation of the critical conditions for DRX.

@@

The material used for this study is a medium-carbon steel with the chemical composition presented in Table \ref{tab:Composition}.
\begin{table}[H]
\centering
\caption{Chemical composition of medium carbon steel. Fe = balance.}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{LCCCCCCC}
\toprule
\textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\
\toprule
\textbf{Wt~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
\bottomrule
\end{tabularx}
\label{tab:Composition}
\end{table}
Hot compression tests were conducted on cylinders with an initial diameter of $\phi=10$~mm and a height of $h=15$~mm using a Gleeble-3800 thermomechanical simulator.
The tests were conducted at 5 temperature levels (ranging from $1050\celsius$ to $1250\celsius$) and 6 strain rates (ranging from $0.001~\ps$ to $5~\ps$).
The imposed displacement was set to $d=6$~mm, resulting in a reduction of $40\%$ of the initial height.
To reduce friction during testing, thin tantalum sheets were used as a lubricant on the contact surface of the anvils and specimens.
In order to remove thermal gradients, the samples were heated at a speed of $2$\celsius/s until reaching a temperature of $1260\celsius$, then held at that temperature for $5$~minutes.
They were subsequently cooled down to the test temperature at a speed of $1$\celsius/s and left at a consistent temperature for $1$~minute prior to being formed.
During compression, the sample temperature is maintained at a constant level through the machine's thermal control system.
Subsequently, the structure is frozen at a fast pace in order to preserve the microstructure for future analysis.

@@

No activation function was used for the output neuron of the ANN, as is typically omitted in regression applications.
The chosen architecture for our application consists of two hidden layers, one with 7 neurons and the other with 5 neurons, as illustrated in Figure \ref{fig:ANN-7-5}.
To calculate the number of internal parameters $N_{int}$ in the model, where $n$ and $m$ represent the number of neurons in the first and second hidden layers, respectively, the following formula may be used: $N_{int}=m(2+n)+2n+1$.
So that for a $7-5$ network, $N_{int}=60$.
\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/ANN-7-5}
\caption{Two hidden layers artificial neural network architecture with 1 input neuron (green) and 1 output neuron (red).}
\label{fig:ANN-7-5}
\end{figure}
The Python program used for training the neural network was created with the dedicated Python library, Tensorflow \cite{Abadi-2016}.
The training phase employed the Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015}.
The training was conducted using $50,000$ epochs of the experimental dataset.
It took approximately 15 minutes to train the ANN model on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64-bit with 16 GB of RAM and an Intel 4-core i7-10510U processor until the converged parameters were obtained.

@@

It is evident that using the ANN model to depict the $\sigma(\varepsilon)$ curve is superior to using an $11^{th}$ order polynomial fit, as demonstrated by the lower estimated error.
Thus, this architecture of the ANN model is used for all subsequent curves, resulting in the deduction of the hardening curves, which illustrate the stress change rate relative to strain ($\frac{\partial \sigma}{\partial \varepsilon}$).
An illustration of computing the hardening curve $\theta(\sigma)$ for a single temperature is displayed in Figure \ref{fig:AnnTheta}. The blue line represents the direct calculation of the derivative of the raw stress versus strain, whereas the red line represents the derivative of the stress filtered by the neural network versus strain.
An overview of the remaining temperatures can be found in Figure \ref{fig:nThetaOP}. \OP{Have to improve this later} \textcolor{red}{Okay}.
The identical process applies to all 20 stress/strain curves.
These curves deliver essential data regarding the critical stresses and strains required for predicting DRX in the subsequent analysis.

@@

\begin{table}[h!]
\centering
\caption{Critical conditions based on the proposed approach.\OP{Caption changed} \textcolor{red}{Okay}}\vspace{-1mm}
\begin{tabular}{cccccc}
\toprule
$\mdot{\varepsilon}$ ($\ps$) & $T$ (\celsius) & $\varepsilon_p$ & $\sigma_p$ (MPa) &  $\varepsilon_c$ & $\sigma_c$ (MPa) \\
\toprule
 & $1050$ & $0.178$ & $37.862$ & $0.083$ & $33.050$\\
 & $1100$ & $0.143$ & $29.770$ & $0.067$ & $25.648$\\
$0.001$ & $1150$ & $0.124$ & $23.330$ & $0.051$ & $19.116$\\
 & $1200$ & $0.102$ & $19.373$ & $0.039$ & $16.244$\\
 & $1250$ & $0.084$ & $13.883$ & $0.035$ & $11.302$\\
\hline
 & $1050$ & $0.281$ & $57.915$ & $0.131$ & $51.602$\\
 & $1100$ & $0.228$ & $46.107$ & $0.108$ & $40.495$\\
$0.01$ & $1150$ & $0.195$ & $38.249$ & $0.086$ & $33.435$\\
 & $1200$ & $0.172$ & $30.991$ & $0.076$ & $26.718$\\
 & $1250$ & $0.139$ & $24.739$ & $0.051$ & $20.004$\\
\hline
 & $1050$ & $0.571$ & $91.413$ & $0.244$ & $83.814$\\
 & $1100$ & $0.430$ & $72.662$ & $0.194$ & $65.259$\\
$0.1$ & $1150$ & $0.344$ & $57.774$ & $0.160$ & $51.723$\\
 & $1200$ & $0.299$ & $48.473$ & $0.136$ & $42.386$\\
 & $1250$ & $0.259$ & $40.195$ & $0.119$ & $35.277$\\
\hline
 & $1050$ & $0.700$ & $127.17$ & $0.577$ & $116.10$\\
 & $1100$ & $0.700$ & $106.61$ & $0.329$ & $94.510$\\
$1$ & $1150$ & $0.700$ & $89.525$ & $0.268$ & $89.067$\\
 & $1200$ & $0.700$ & $72.270$ & $0.178$ & $57.929$\\
 & $1250$ & $0.393$ & $59.992$ & $0.112$ & $54.066$\\
\bottomrule
\end{tabular}
\label{tab:OPparams}
\end{table}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/picDRX}
\caption{Schematic diagram of three stages during DRX, nucleation, nucleus growth and grain contact.% \OP{Is it a copy/paste from a publication? If so, you can't put it as it!} \textcolor{red}{Of course it was taken from publication as reference is mentioned. Please, I will appreciate if you could rearrange it as it would have been made. Thanks !}
}
\label{fig:DRXschema}
\end{figure}
\OP{See the new proposed figure 6}

The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
The predicted volumetric fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model  \cite{wan2017experimental} \OP{REF?} \textcolor{red}{Done}, commonly known as the JMAK model, expressed by the following equation:
\begin{equation}
X_{drx}^{p} = 1 - \exp\left[ -k\left(\frac{\varepsilon - \varepsilon_c}{\varepsilon_p}\right)^{n_k}\right]
\label{eq:drxpred}
\end{equation}
With $\varepsilon_c$ and $\varepsilon_p$ as the critical and peak strain respectively; $k$ and $n_k$ as the model's parameters and the experimental equivalence of this volumic fraction of DRX is given by :
\begin{equation}
X_{drx}^{e} = \frac{\sigma_p-\sigma}{\sigma_p-\sigma_{s}}
\label{eq:drxexp}
\end{equation}

@@

The curves of $X_{drx}(\varepsilon)$ are provided in Figure \ref{fig:nDRX} using the critical conditions calculated by the Poliak method.
From this figure, it can be observed that the predictions align well with the experimental data, thus demonstrating the validity of the used model. \OP{I don't agree!} \textcolor{red}{Please have a look on Figure \ref{fig:nDRX} for more comprehension}
These results will therefore be used subsequently in the simulation section.
\begin{figure}[H]
\centering
\includegraphics[width=0.99\columnwidth]{Figures/nDRX1}
\caption{Comparison between DRX experimental data and JMAK model based prediction. \OP{I don't see the comparison? Is there many superposed curves ???} \textcolor{red}{As I said in my previous mail, I was writing the paper like the experimental data are already provided. Everything is okay now, I think !}}
\label{fig:nDRX}
\end{figure}
\OP{I think this is not finished yet ?}

@@

In this section, we will focus on numerically validating the previously performed identification of dynamic recrystallization.
This requires establishing a constitutive law capable of accurately predicting the material's plastic deformation.
In our previous publication (Tize Mha \eal \cite{TizeMha-2023}), we conducted a comparison between analytical constitutive laws and a neural network-based approach.
The results revealed an artificial neural network model as the most appropriate option for this material.
As a result, this section has two main focuses: first, a summary of the ANN-based constitutive law identification, as previously presented; and second, the incorporation of this identified ANN model with the JMAK model to predict dynamic recrystallization behavior.

@@

In general terms, flow stress $\sigma$ is a non-linear function of the strain $\varepsilon$, increasing with the strain rate $\mdot\varepsilon$, but decreasing with increasing temperature $T$.
This model can be described as an elastoplastic model that takes into consideration the influence of temperature and strain rate.
This type of behavior generally leads to Johnson--Cook \cite{Johnson-1983}, Zerilli--Armstrong \cite{Zerilli-1987}, Hansel--Spittel \cite{Hensel-1978} or Arrhenius \cite{Sellars-1966} flow law type.
Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.

As stated in the research conducted by Tize Mha \eal \cite{TizeMha-2023}, the Johnson--Cook, Zerilli--Armstrong, or Hansel--Spittel models provide an estimate of material behavior at strain rates exceeding $1~\ps$, but they neglect the softening due to DRX that is evident on experimental curves for strain rates below $1~\ps$, as presented in Figure \ref{fig:RawData}.
Indeed, at the lowest strain rates, the flow stress $\sigma$ increases with strain $\varepsilon$ until reaching a value of roughly $\varepsilon=0.2$ to $0.3$. 
Afterward, it decreases, maintaining a relatively constant value until the end of the compression test.
The Arrhenius model is the only one that can somewhat explain this softening at low strain rates.
As proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023} and Tize Mha \eal \cite{TizeMha-2023}, an effective alternative is to use a flow law defined by an artificial neural network trained directly on experimental data from compression tests.
Properly defining the hyperparameters of this neural network, such as the number of hidden layers, number of neurons, and activation functions, enables us to obtain a flow law that accurately replicates the data acquired from compression tests.

According to the method proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023}, we have developed a two-hidden-layer artificial neural network based flow law in Tize Mha \eal \cite{TizeMha-2023}. 
Figure \ref{fig:ANN-2HL} shows the general structure of this ANN. 
The input layer of the ANN consists of three neurons that correspond to the model inputs, which are $\varepsilon$, $\mdot\varepsilon$, and $T$. 
The output layer of the ANN contains one neuron representing $\sigma$, while there are two hidden layers.
All details regarding the artificial neural network, experimental data setup, and training method are detailed in the paper proposed by Pantalé \cite{Pantale-2023}.

@@

We again used the Tensorflow library to develop the training program and employed the ADAM optimizer for the training phase.
The training database, as described in Section \ref{subsec:ExperimentalProcedure}, contains $21,030$ quadruples of values for strain ($\varepsilon$), strain rate ($\mdot\varepsilon$), temperature ($T$), and stress ($\sigma$).

We selected six different networks, named 3-$n$-$m$-1, where $n$ represents the number of neurons in the first hidden layer and $m$ indicates the number of neurons in the second hidden layer to demonstrate the significance of choosing the appropriate number of neurons in these two layers.

The training was conducted based on $5,000$ epochs of the experimental dataset.
It took 40 minutes to train the ANN model on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64-bit operating system with 16 GB of RAM and an Intel 4-core i7-10510U processor until obtaining the converged parameters.

Figure \ref{fig:ANN-conv} shows the evolution of the training error, defined by the $\log_{10}$ of the internal $\RMSE$, during the training phase.
Table \ref{tab:Errors} summarizes the final values of this criterion, as well as the final values of the $\MARE$ and the $\RMSE$ for all six neural network configurations.
Based on these results, the 3-15-7-1 network was chosen for further investigation. 
This network exhibited the most efficient convergence and achieved the lowest final error values of $\MARE=0.62\%$ and $\RMSE=0.38~\MPa$, while also maintaining a reasonable number of internal parameters ($N_{int}=180$).

@@

\begin{table}[H]
\caption{Architecture and accuracy coefficients for all the proposed networks.}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\begin{tabularx}{\textwidth}{LCCCCCC}
\toprule
\textbf{Coefficients} & \textbf{3-7-5-1} & \textbf{3-9-4-1} & \textbf{3-9-5-1} & \textbf{3-9-7-1} & \textbf{3-13-7-1} & \textbf{3-15-7-1} \\
\toprule
$N_{int}$ & $74$ & $81$ & $92$ & $114$ & $158$ &$180$\\
\hline
$\log_{10}(\RMSE)$ & $-2.40$ & $-2.42$ & $-2.38$ & $-2.45$ & $-2.50$ & $-2.58$ \\
$\MARE(\%)$ & $1.13$ & $1.05$ & $1.08$ & $0.91$ & $0.75$ & $0.62$ \\
$\RMSE(\MPa)$ & $0.59$ & $0.57$ & $0.65$ & $0.55$ & $0.46$ & $0.38$ \\
\bottomrule
\end{tabularx}
\label{tab:Errors}
\end{table}

\begin{figure}[H]
\centering
\includegraphics[width=0.9\columnwidth]{Figures/CompExpANN-3-15-7-1}
\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma$ by the 3-15-7-1 ANN model.}
\label{fig:ANN-3-15-7-1}
\end{figure}
This model will serve as the material flow equation for the numerical simulations discussed in Section \ref{subsec:DRXSimulation}.

@@

To evaluate the effectiveness of the DRX model presented earlier, we propose a numerical simulation of a compression test in this section.
Our simulation concerns a medium-carbon P20 iron alloy, the same material used for the model's identification.
An axisymmetric Finite Element (FE) model of hot cylinder compression with a height of $h=15$~mm and a diameter of $\phi=10$~mm is used, as shown in Figure \ref{fig:Mesh}.
The assumed friction coefficient at the material/die interface is $\mu=0.2$ \cite{zhang2019elevated,sun2020kinetics}.
The mesh is composed of $986$ ($17\times58$) CAX4R elements (4-node axisymmetric bi-linear quadrilateral elements with reduced integration and hourglass control).
Abaqus/Implicit is used to run the FE model simulation because of the long time needed to simulate a low strain rate compression.
A displacement of $60\%, ~45\%, ~30\%$ and $15\%$ of the total height is imposed on the upper part of the cylinder along the vertical axis of the specimen during compression.
The upper and the lower parts of the specimen can slip in the radial direction according to the friction coefficient and the contact conditions. The axial displacement ($u_z$) of the upper part is imposed with a fixed velocity while the axial displacement of the lower part remains fixed during the simulation.
The simulation evaluated the impact of reducing the cylinder height with the effects of strain rate and temperature. 
Conclusions were drawn based on this analysis.
The simulation considered three temperatures ($1050\degree$C, $1150\degree$C, and $1250\degree$C) and four strain rates ($0.001~\ps$, $0.01~\ps$, $0.1~\ps$, and $1.0~\ps$).
\begin{figure}[H]
\centering
\includegraphics[height=0.7\columnwidth]{Figures/CyCompression2}
\caption{Numerical FE model for the simulation of the compression test.}
\label{fig:Mesh}
\end{figure}

@@

In this study, we used the abilities of the ANN technique to deeply comprehend the dynamic recrystallization process and its adaptations in varying conditions.
Through the fusion of ANN modeling, fundamental material models, simulation software, and experimental confirmation, a comprehensive framework has been created that greatly enhances the materials science and engineering field.
Initially, we successfully used an ANN model to efficiently filter flow stress curves, which enabled us to predict critical conditions using the Poliak model.
This allows us to accurately anticipate the conditions at which the DRX process begins, providing a valuable tool for predicting material behavior under specific deformation scenarios.
